Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-24 conclusions.tex
Minor rewording in conclusion
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1156 ccdd05d5-56c1-461a-bf98-85f6876523b4

Although we have demonstrated a computationally feasible detection statistic for
advance detection, we have not yet explored data whitening, triggering,
coincidence, and ranking of gravitational wave candidates in a framework that
supports early \EM\ followup.  One complication in deploying a low-latency or
early-warning search is that whitening the detector data involves estimating the
noise power spectrum, which is often done in acausally.  We will have to look into
causal or low latency alternatives to conventional spectral estimation techniques.
Another potential complication is that if adjacent time slices have non-negligible
cross-correlation with each other, then there may be some subtleties in the design
of the triggering and coincidence stages that we must address in order to translate
the early-warning outputs into candidate events.  The time-slice decomposition and
the \SVD\ may also be beneficial for the postprocessing stage because they will
help us form low-latency signal-based vetoes (e.g. $\chi^2$ statistics)
that have been essential for glitch rejection used in previous \GW{} \CBC{}
searches.

>>>>

Although we have demonstrated a computationally feasible detection statistic for
advance detection, we have not yet explored data whitening, triggering,
coincidence, and ranking of gravitational wave candidates in a framework that
supports early \EM\ followup.  One complication in deploying a low-latency or
early-warning search is that whitening the detector data involves estimating the
noise power spectrum, which is often done in acausally.  We will have to look into
causal or low latency alternatives to conventional spectral estimation techniques.
Another potential complication is that if adjacent time slices have non-negligible
cross-correlation with each other, then there may be some subtleties in the design
of the triggering and coincidence stages that we must address in order to translate
the early-warning outputs into candidate events.  On the other hand, the time-slice
decomposition and the \SVD\ may be beneficial for the postprocessing stage
because they will help us form low-latency signal-based vetoes (e.g. $\chi^2$ statistics)
that have been essential for glitch rejection used in previous \GW{} \CBC{}
searches.
